InteroceptionScale - Data Analysis

### 2024-12-18 study1/analysis/2_analysis.qmd
finalize analysis

```{r}
#| fig-width: 10
#| fig-height: 10
#| eval: true

@@

higher <- make_loadingtable(t(net.loads(ega3$EGA$higher_order)$std))
cluster_order <- names(higher)[!names(higher) %in% c("Item", "Cluster", "Max")]

lower <- make_loadingtable(net.loads(ega3$EGA$lower_order)$std) |>
  select(names(higher)) |>
  mutate(Cluster = fct_relevel(Cluster, cluster_order)) |>
  arrange(Cluster, desc(Max))

higher$Item <- paste0("H", higher$Item)
higher$Label <- paste("TODO", 1:nrow(higher))
lower <- mutate(lower, Label = labels[Item], ID= Item, Item = 1:n())

rbind(higher, select(lower, -ID)) |>

@@

  # datawizard::data_rename(c(XC1 = "C01", XC2 = "C02")) |> 

@@

    locations = gt::cells_body(columns="Label")

@@

  gt::cols_width(Label ~ gt::pct(30)) |>
  gt::gtsave("table1.html", inline_css = TRUE) # Save it and reload it otherwise formatting not ideal

<object type="text/html" data="table1.html" width="120%" height="1000"></object>

@@

# Arrange lower nodes in circle
lower_nodes <- graph$nodes |> 
  filter(level == "Lower") |> 
  mutate(name = fct_relevel(name, as.character(lower$ID)),
         ID = name) |> 
  arrange(name)  
lower_edges <- graph$edges |> 
  filter(from %in% lower_nodes$name & to %in% lower_nodes$name)
lower_layout <- tidygraph::tbl_graph(lower_nodes, edges=lower_edges, directed=FALSE) |> 
  ggraph::create_layout(layout = 'circle')
rownames(lower_layout) <- lower_nodes$name

# Arrange higher nodes in circle
higher_nodes <- graph$nodes |> 
  filter(level == "Higher") |> 
  mutate(ID = name,
         name = replace_highernames(name),
         name = fct_relevel(name, names(select(higher, -Item, -Cluster,-Max,-Label)))) |>
  arrange(name)
higher_edges <- graph$edges |> 
  filter(from %in% higher_nodes$name & to %in% higher_nodes$name)
higher_layout <- tidygraph::tbl_graph(higher_nodes, edges=higher_edges, directed=FALSE) |> 
  ggraph::create_layout(layout = 'circle')
rownames(higher_layout) <- higher_nodes$ID

# Put circles together
layout <- tidygraph::tbl_graph(graph$nodes, edges=graph$edges, directed=FALSE) |> 
  ggraph::create_layout(layout = 'linear', circular = TRUE)
layout[layout$level == "Lower", "x"] <- lower_layout[layout[layout$level == "Lower", "name"], "x"]
layout[layout$level == "Lower", "y"] <- lower_layout[layout[layout$level == "Lower", "name"], "y"]
layout[layout$level == "Higher", "x"] <- higher_layout[layout[layout$level == "Higher", "name"], "x"] * 0.5
layout[layout$level == "Higher", "y"] <- higher_layout[layout[layout$level == "Higher", "name"], "y"] * 0.5
layout[layout$level == "Lower", "name"] <- replace_lowernames(layout[layout$level == "Lower", "name"], lower)
layout[layout$level == "Higher", "name"] <- replace_highernames(layout[layout$level == "Higher", "name"])

@@

ggraph(layout) +
  geom_edge_link(aes(edge_alpha=as.numeric(type == "virtual"), edge_width = abs(link)), edge_width=0.2, color="grey") +
  geom_edge_arc(aes(edge_color = link, edge_width = abs(link), edge_alpha=as.numeric(type == "real"))) +
  geom_node_point(aes(color=dimension, shape=level), size=12) +
  geom_node_text(aes(label=name), fontface="bold") +
  # geom_node_text(aes(label = dimmension_label, angle = node_angle(x, y), hjust = 'outward')) +
  scale_edge_alpha(range = c(0, 0.9), guide="none") +
  scale_edge_width(range = c(0.2, 3), guide="none") +
  scale_edge_colour_gradientn(colors=c("#E53935", "#E53935", "white", "#43A047", "#43A047"), 
                              values=c(-1, -0.5, 0, 0.5, 1), guide="none") +
  scale_shape_manual(values=c("Higher"="square", "Lower"="circle"), guide="none") +
  scale_color_manual(values=c(
    "H1"="#90CAF9", "H2"="#C5E1A5", "H3"="#EF9A9A", 
    "L1"="#B39DDB", "L9"="#9FA8DA", "L13"="#90CAF9", "L18"="#81D4FA", "L3"="#80DEEA",
    "L4"="#F3F29D", "L6"="#E6EE9C", "L15"="#D6E8A1", "L8"="#C5E1A5", "L10"="#B5DCA6", "L5"="#A5D6A7", "L2"="#93D1B6",
    "L17"="#CE93D8", "L14"="#F48FB1", "L12"="#EF9A9A", "L16"="#FFAB91", "L11"="#FFCC80", "L7"="#FFE082"),
                     breaks=c("H1", "H2", "H3")) +
  theme_void() +
  labs(color="Metaclusters")
```

>>>>

@@

dimensions <- list(
  C01 = "UrIn",       # Urointestinal Inaccuracy
  C09 = "CaCo",       # Cardiorespiratory Confusion
  C13 = "CaNo",       # Cardiorespiratory Noticing
  C18 = "Olfa",       # Olfactory Compensation
  C03 = "Sati",       # Satiety Noticing
  C04 = "SexA",       # Sexual Arousal Awareness
  C06 = "SexS",       # Sexual Arousal Sensitivity
  C15 = "SexO",       # Sexual Organs Sensitivity
  C08 = "UrSe",       # Urointestinal Sensitivity
  C10 = "RelA",       # Relaxation Awareness
  C05 = "StaS",       # State Specificity
  C02 = "ExAc",       # Expulsion Accuracy
  C17 = "Card",       # Cardioception
  C14 = "Resp",       # Respiroception
  C12 = "Sign",       # Signalling
  C16 = "Gast",       # Gastroception
  C11 = "Derm",       # Dermatoception
  C07 = "SexC"        # Sexual Arousal Changes
)

higher <- make_loadingtable(t(net.loads(ega3$EGA$higher_order, loading.method="revised")$std))
cluster_order <- names(higher)[!names(higher) %in% c("Item", "Cluster", "Max")]

lower <- make_loadingtable(net.loads(ega3$EGA$lower_order, loading.method="revised")$std) |>
  select(names(higher)) |>
  mutate(Cluster = fct_relevel(Cluster, cluster_order)) |>
  arrange(Cluster, desc(Max))

higher$Item <- paste0("M", higher$Item)
higher$Label <- c("Interoceptive Deficit", "Interoceptive Awareness", "Interoceptive Sensitivity")
lower <- mutate(lower, Label = labels[Item], ID= Item, Item = 1:n())

tab1 <- rbind(higher, select(lower, -ID)) |>

@@

  # datawizard::data_rename(dimensions) |>  # https://github.com/easystats/datawizard/issues/576
  datawizard::data_rename(names(dimensions), dimensions) |> 
  mutate(`|` = "") |> 

@@

    locations = gt::cells_body(columns="Label", rows=c(4:57))

@@

  gt::cols_width(Label ~ gt::pct(66),
                 `|` ~ gt::pct(1))

gt::gtsave(gt::cols_hide(tab1, `|`), "table1.html", inline_css = TRUE) # Save it and reload it otherwise formatting not ideal

Sys.setenv(CHROMOTE_CHROME = "C:\\Program Files (x86)\\Microsoft\\Edge\\Application\\msedge.exe")

gt::gtsave(tab1, "table1.png", vwidth=1660, expand=0, quiet=TRUE)
```

<object type="text/html" data="table1.html" width="125%" height="1000"></object>

<!-- ![](table1.png) -->

@@

# Arrange lower nodes in circle
lower_nodes <- graph$nodes |> 
  filter(level == "Lower") |> 
  mutate(name = fct_relevel(name, as.character(lower$ID)),
         ID = name) |> 
  arrange(name)  
lower_edges <- graph$edges |> 
  filter(from %in% lower_nodes$name & to %in% lower_nodes$name)
lower_layout <- tidygraph::tbl_graph(lower_nodes, edges=lower_edges, directed=FALSE) |> 
  ggraph::create_layout(layout = 'circle') |> 
  as.data.frame()
rownames(lower_layout) <- lower_nodes$name

# Arrange higher nodes in circle
higher_nodes <- graph$nodes |> 
  filter(level == "Higher") |> 
  mutate(ID = name,
         name = replace_highernames(name),
         name = fct_relevel(name, names(select(higher, -Item, -Cluster,-Max,-Label)))) |>
  arrange(name)
higher_edges <- graph$edges |> 
  filter(from %in% higher_nodes$name & to %in% higher_nodes$name)
higher_layout <- tidygraph::tbl_graph(higher_nodes, edges=higher_edges, directed=FALSE) |> 
  ggraph::create_layout(layout = 'circle') |> 
  as.data.frame()
rownames(higher_layout) <- higher_nodes$ID

# Put circles together
layout <- tidygraph::tbl_graph(graph$nodes, edges=graph$edges, directed=FALSE) |> 
  ggraph::create_layout(layout = 'linear', circular = TRUE)
layout[layout$level == "Lower", "x"] <- lower_layout[layout[layout$level == "Lower", ]$name, "x"]
layout[layout$level == "Lower", "y"] <- lower_layout[layout[layout$level == "Lower", ]$name, "y"]
layout[layout$level == "Higher", "x"] <- higher_layout[layout[layout$level == "Higher", ]$name, "x"] * 0.5
layout[layout$level == "Higher", "y"] <- higher_layout[layout[layout$level == "Higher", ]$name, "y"] * 0.5
layout[layout$level == "Lower", "name"] <- replace_lowernames(layout[layout$level == "Lower", ]$name, lower)
layout[layout$level == "Higher", "name"] <- replace_highernames(layout[layout$level == "Higher", ]$name)

# Final renaming
layout[layout$level == "Higher", "name"] <- unlist(dimensions)[layout[layout$level == "Higher", ]$name]
layout[layout$level == "Higher", "dimension"] <- layout[layout$level == "Higher", ]$dimension |> 
  str_replace("H1", "Deficit") |> 
  str_replace("H2", "Awareness") |> 
  str_replace("H3", "Sensitivity")

@@

ggraph(layout) +
  geom_edge_link(aes(edge_alpha=as.numeric(type == "virtual"), edge_width = abs(link)), edge_width=0.2, color="grey") +
  geom_edge_arc(aes(edge_color = link, edge_width = abs(link), edge_alpha=as.numeric(type == "real"))) +
  geom_node_point(aes(color=dimension, shape=level), size=12) +
  geom_node_text(aes(label=name), fontface="bold") +
  # geom_node_text(aes(label = dimmension_label, angle = node_angle(x, y), hjust = 'outward')) +
  scale_edge_alpha(range = c(0, 0.9), guide="none") +
  scale_edge_width(range = c(0.2, 3), guide="none") +
  scale_edge_colour_gradientn(colors=c("#E53935", "#E53935", "white", "#43A047", "#43A047"), 
                              values=c(-1, -0.5, 0, 0.5, 1), guide="none") +
  scale_shape_manual(values=c("Higher"="square", "Lower"="circle"), guide="none") +
  scale_color_manual(values=c(
    "Deficit"="#90CAF9", "Awareness"="#C5E1A5", "Sensitivity"="#EF9A9A", 
    "L1"="#B39DDB", "L9"="#9FA8DA", "L13"="#90CAF9", "L18"="#81D4FA", "L3"="#80DEEA",
    "L4"="#F3F29D", "L6"="#E6EE9C", "L15"="#D6E8A1", "L8"="#C5E1A5", "L10"="#B5DCA6", "L5"="#A5D6A7", "L2"="#93D1B6",
    "L17"="#CE93D8", "L14"="#F48FB1", "L12"="#EF9A9A", "L16"="#FFAB91", "L11"="#FFCC80", "L7"="#FFE082"),
                     breaks=c("Deficit", "Awareness", "Sensitivity")) +
  theme_void() +
  theme(legend.title = element_text(face="bold")) +
  labs(color="Metaclusters")
```
